---
title: APS Baseline
author: ""
date: today
format:
    dashboard:
        logo: /assets/graphics/detect-logo.png
        theme: simplex
        orientation: columns
---

```{r}
#| label: set up data and libraries
#| echo: false

library(dplyr)
library(DT)
library(duckdb)
library(plotly)
library(tidyr)

# source the codebook
source(here::here("r", "codebook.r"))

DATA <- fs::as_fs_path(here::here("data", "aps_baseline", "APS-DATA.duckdb"))

con <- dbConnect(duckdb(), dbdir = DATA, read_only = TRUE)
```

# {.sidebar}

Dashboard last updated: {{< meta date >}}

# Submission Details {orientation="rows"}

```{r}
#| label: submission value box data
#| echo: false

total_subs <- dbGetQuery(
    con,
    "SELECT 
        COUNT(*) AS total_subs
    FROM 'APS-BL';
    "
)

total_sites <- dbGetQuery(
    con,
    "SELECT 
        COUNT(DISTINCT ar_institution) as total_sites
    FROM 'APS-BL';
    "
)

total_champs <- dbGetQuery(
    con,
    "SELECT 
        COUNT(DISTINCT ar_user) as total_champs
    FROM 'APS-BL';
    "
)
```

## Row
```{r}
#| label: valuebox total submissions
#| title: Total Submissions
#| content: valuebox

list(
    icon = "file-check-fill",
    color = "success",
    value = total_subs$total_subs
)
```

```{r}
#| label: valuebox total sites
#| title: Total Sites
#| content: valuebox

list(
    icon = "hospital-fill",
    color = "info",
    value = total_sites$total_sites
)
```

```{r}
#| label: valuebox total site champions
#| title: Total Site Champions
#| content: valuebox

list(
    icon = "person-arms-up",
    color = "warning",
    value = total_champs$total_champs
)
```

## Row

```{r}
#| label: bar plot subs by site
#| echo: false
#| fig-cap: Total Submissions by Institution and Site Champion

# query the data
subs_by_site <- as.data.frame(dbGetQuery(
    con,
    "SELECT COUNT(form_id) AS total_subs, ar_user AS site_champ, ar_institution AS institution FROM 'APS-BL' GROUP BY ar_user, ar_institution ORDER BY total_subs DESC;"
))

# replace uninformative columns with string names
subs_by_site <- subs_by_site |>
    left_join(user, by = "site_champ") |>
    left_join(institution, by = "institution") |>
    select(total_subs, site_champ_label, institution_label)

chart_1 <- ggplot(
    data = subs_by_site,
    aes(x = total_subs, y = institution_label, fill = site_champ_label)
) +
    geom_col() +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_manual(values = colors_user)

ggplotly(chart_1, tooltip = c("x", "fill"))
```

```{r}
#| label: scatter plot subs by site over time
#| echo: false
#| fig-cap: Total Submissions by Institution over Time

# query the data
subs_over_time <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        form_id AS sub,
        ar_institution AS institution,
        ar_aps_report_date AS date,
        COUNT(*) OVER (
    ORDER BY
        ar_aps_report_date
        ROWS BETWEEN UNBOUNDED PRECEDING AND CURRENT ROW
    ) AS cum_submissions
    FROM
	    'APS-BL'
    WHERE
	    ar_aps_report_date IS NOT NULL
    ORDER BY
	    date
    "
))

# replace uninformative columns with string names
subs_over_time <- subs_over_time |>
    left_join(institution, by = "institution") |>
    select(sub, cum_submissions, date, institution_label)

chart_2 <- ggplot(
    data = subs_over_time,
    aes(x = date, y = cum_submissions, color = institution_label)
) +
    geom_point() +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_color_manual(values = colors_institution)

ggplotly(chart_2)
```

# Randomization Details

## Row {.tabset}

```{r}
#| label: randomized submissions value box data
#| echo: false

# total submissions by randomization status
total_subs_by_rand_sql <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT clinician_id, COUNT(form_id) as num
    FROM (
        SELECT ar_clinician_bcm as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_bcm IS NOT NULL
        UNION ALL
        SELECT ar_clinician_jh as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_jh IS NOT NULL
        UNION ALL
        SELECT ar_clinician_ucsf as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_ucsf IS NOT NULL
        UNION ALL
        SELECT ar_clinician_uab as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_uab IS NOT NULL
        UNION ALL
        SELECT ar_clinician_utsw as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_utsw IS NOT NULL
        UNION ALL
        SELECT ar_clinician_lbj as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_lbj IS NOT NULL
        UNION ALL
        SELECT ar_clinician_utp as clinician_id, form_id FROM 'APS-BL' WHERE ar_clinician_utp IS NOT NULL
    ) as combined
    GROUP BY clinician_id;
    "
))

all_clinicians <- rbind(
    bcm_clinician,
    jh_clinician,
    ucsf_clinician,
    uab_clinician,
    utsw_clinician,
    lbj_clinician,
    utp_clinician
)

no_site_champs <- all_clinicians |>
    filter(!clinician_name %in% user$site_champ_label[1:7])

total_subs_by_rand <- total_subs_by_rand_sql |>
    left_join(all_clinicians, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

total_subs_by_rand <- total_subs_by_rand |>
    group_by(clinician_randomized) |>
    summarise(num = sum(num))

total_subs_by_rand_no_sc <- total_subs_by_rand_sql |>
    left_join(no_site_champs, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

total_subs_by_rand_no_sc <- total_subs_by_rand_no_sc |>
    group_by(clinician_randomized) |>
    drop_na() |>
    summarise(num = sum(num))
```

```{r}
#| label: pre-launch randomized submissions value box data
#| echo: false

# pre-launch submission by randomization status
pre_total_subs_by_rand_sql <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT clinician_id, COUNT(form_id) AS num
    FROM (
        SELECT ar_clinician_bcm AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_bcm IS NOT NULL AND ar_aps_report_date < '2025-03-26'
        UNION ALL

        SELECT ar_clinician_jh AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_jh IS NOT NULL AND ar_aps_report_date < '2025-04-04'
        UNION ALL

        SELECT ar_clinician_ucsf AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_ucsf IS NOT NULL AND ar_aps_report_date < '2025-03-26'
        UNION ALL

        SELECT ar_clinician_uab AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_uab IS NOT NULL AND ar_aps_report_date < '2025-03-18'
        UNION ALL

        SELECT ar_clinician_utsw AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_utsw IS NOT NULL AND ar_aps_report_date < '2025-04-04'
        UNION ALL

        SELECT ar_clinician_lbj AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_lbj IS NOT NULL AND ar_aps_report_date < '2025-03-26'
        UNION ALL

        SELECT ar_clinician_utp AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_utp IS NOT NULL AND ar_aps_report_date < '2025-03-13'
    ) AS combined
    GROUP BY clinician_id;
    "
))

pre_total_subs_by_rand <- pre_total_subs_by_rand_sql |>
    left_join(all_clinicians, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

pre_total_subs_by_rand <- pre_total_subs_by_rand |>
    group_by(clinician_randomized) |>
    summarise(num = sum(num))

pre_total_subs_by_rand_no_sc <- pre_total_subs_by_rand_sql |>
    left_join(no_site_champs, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

pre_total_subs_by_rand_no_sc <- pre_total_subs_by_rand_no_sc |>
    group_by(clinician_randomized) |>
    drop_na() |>
    summarise(num = sum(num))
```

```{r}
#| label: post-launch randomized submissions value box data
#| echo: false

# post-launch submission by randomization status
post_total_subs_by_rand_sql <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT clinician_id, COUNT(form_id) AS num
    FROM (
        SELECT ar_clinician_bcm AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_bcm IS NOT NULL AND ar_aps_report_date >= '2025-03-26'
        UNION ALL

        SELECT ar_clinician_jh AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_jh IS NOT NULL AND ar_aps_report_date >= '2025-04-04'
        UNION ALL

        SELECT ar_clinician_ucsf AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_ucsf IS NOT NULL AND ar_aps_report_date >= '2025-03-26'
        UNION ALL

        SELECT ar_clinician_uab AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_uab IS NOT NULL AND ar_aps_report_date >= '2025-03-18'
        UNION ALL

        SELECT ar_clinician_utsw AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_utsw IS NOT NULL AND ar_aps_report_date >= '2025-04-04'
        UNION ALL

        SELECT ar_clinician_lbj AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_lbj IS NOT NULL AND ar_aps_report_date >= '2025-03-26'
        UNION ALL

        SELECT ar_clinician_utp AS clinician_id, form_id FROM 'APS-BL'
        WHERE ar_clinician_utp IS NOT NULL AND ar_aps_report_date >= '2025-03-13'
    ) AS combined
    GROUP BY clinician_id;
    "
))

post_total_subs_by_rand <- post_total_subs_by_rand_sql |>
    left_join(all_clinicians, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

post_total_subs_by_rand <- post_total_subs_by_rand |>
    group_by(clinician_randomized) |>
    summarise(num = sum(num))

post_total_subs_by_rand_no_sc <- post_total_subs_by_rand_sql |>
    left_join(no_site_champs, by = "clinician_id") |>
    select(num, clinician_name, clinician_randomized)

post_total_subs_by_rand_no_sc <- post_total_subs_by_rand_no_sc |>
    group_by(clinician_randomized) |>
    drop_na() |>
    summarise(num = sum(num))
```

### Overall

```{r}
#| label: valuebox total submissions by randomized clinicians
#| title: Total Submissions by Randomized Clinicians
#| content: valuebox

list(
    icon = "clipboard-check-fill",
    color = "success",
    value = total_subs_by_rand[
        total_subs_by_rand$clinician_randomized == 1,
    ]$num
)
```

```{r}
#| label: valuebox total submissions by non-randomized clinicians
#| title: Total Submissions by Non-Randomized Clinicians
#| content: valuebox

list(
    icon = "clipboard-x-fill",
    color = "danger",
    value = total_subs_by_rand[
        total_subs_by_rand$clinician_randomized == 0,
    ]$num
)
```

### Launch 

#### Row {height="50%"}

```{r}
#| label: valuebox pre-launch total submissions by randomized clinicians
#| content: valuebox

list(
    icon = "clipboard-check-fill",
    color = "info",
    title = "Pre-launch Total Submissions by Randomized Clinicians",
    value = pre_total_subs_by_rand[
        pre_total_subs_by_rand$clinician_randomized == 1,
    ]$num
)
```

```{r}
#| label: valuebox pre-launch total submissions by non-randomized clinicians
#| content: valuebox

list(
    icon = "clipboard-x-fill",
    color = "info",
    title = "Pre-launch Total Submissions by Non-Randomized Clinicians",
    value = pre_total_subs_by_rand[
        pre_total_subs_by_rand$clinician_randomized == 0,
    ]$num
)
```

```{r}
#| label: valuebox post-launch total submissions by randomized clinicians
#| content: valuebox

list(
    icon = "clipboard-check-fill",
    color = "warning",
    title = "Post-launch Total Submissions by Randomized Clinicians",
    value = post_total_subs_by_rand[
        post_total_subs_by_rand$clinician_randomized == 1,
    ]$num
)
```

```{r}
#| label: valuebox post-launch total submissions by non-randomized clinicians
#| content: valuebox

value <- post_total_subs_by_rand[
    post_total_subs_by_rand$clinician_randomized == 0,
]$num

if (identical(value, numeric(0))) {
    value <- 0
}

list(
    icon = "clipboard-x-fill",
    color = "warning",
    title = "Post-launch Total Submissions by Non-Randomized Clinicians",
    value = value
)
```

#### Row {height="50%"}

```{r}
#| label: valuebox pre-launch total submissions by randomized clinicians no site champs
#| content: valuebox

list(
    icon = "clipboard-check-fill",
    color = "info",
    title = "Pre-launch Total Submissions by Randomized Clinicians (No Site Champions)",
    value = pre_total_subs_by_rand_no_sc[
        pre_total_subs_by_rand_no_sc$clinician_randomized == 1,
    ]$num
)
```

```{r}
#| label: valuebox pre-launch total submissions by non-randomized clinicians no site champs
#| content: valuebox

list(
    icon = "clipboard-x-fill",
    color = "info",
    title = "Pre-launch Total Submissions by Non-Randomized Clinicians (No Site Champions)",
    value = pre_total_subs_by_rand_no_sc[
        pre_total_subs_by_rand_no_sc$clinician_randomized == 0,
    ]$num
)
```

```{r}
#| label: valuebox post-launch total submissions by randomized clinicians no site champs
#| content: valuebox

list(
    icon = "clipboard-check-fill",
    color = "warning",
    title = "Post-launch Total Submissions by Randomized Clinicians (No Site Champions)",
    value = post_total_subs_by_rand_no_sc[
        post_total_subs_by_rand_no_sc$clinician_randomized == 1,
    ]$num
)
```

```{r}
#| label: valuebox post-launch total submissions by non-randomized clinicians no site champs
#| content: valuebox

value <- post_total_subs_by_rand_no_sc[
    post_total_subs_by_rand_no_sc$clinician_randomized == 0,
]$num

if (identical(value, numeric(0))) {
    value <- 0
}

list(
    icon = "clipboard-x-fill",
    color = "warning",
    title = "Post-launch Total Submissions by Non-Randomized Clinicians (No Site Champions)",
    value = value
)
```

### BCM

```{r}
#| label: bcm randomization plot
#| echo: false
#| fig-cap: BCM Submissions by Clinician and Randomization

# query the data
bcm_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_bcm AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 1
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

bcm_random_plot <- bcm_random_plot |>
    left_join(bcm_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_10 <- ggplot(
    data = bcm_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = "stack"
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("03/26/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_10, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: bcm randomization table
#| echo: false
#| tbl-cap: BCM Randomization

bcm_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_bcm AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 1
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

bcm_random_plot <- bcm_random_plot |>
    left_join(bcm_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    bcm_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### JHU
```{r}
#| label: jhu randomization plot
#| echo: false
#| fig-cap: JHU Submissions by Clinician and Randomization

# query the data
jh_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_jh AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 2
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

jh_random_plot <- jh_random_plot |>
    left_join(jh_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_11 <- ggplot(
    data = jh_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = "stack"
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

#TODO: NO VLINE YET SINCE TOOL HAS NOT LAUNCHED

ggplotly(chart_11, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: jhu randomization table
#| echo: false
#| tbl-cap: JHU Randomization

jh_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_jh AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 2
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

jh_random_plot <- jh_random_plot |>
    left_join(jh_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    jh_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### UCSF

```{r}
#| label: ucsf randomization plot
#| echo: false
#| fig-cap: UCSF Submissions by Clinician and Randomization

# query the data
ucsf_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_ucsf AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 3
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

ucsf_random_plot <- ucsf_random_plot |>
    left_join(ucsf_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_12 <- ggplot(
    data = ucsf_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = position_dodge2(width = 10, preserve = "total")
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("04/21/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_12, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: ucsf randomization table
#| echo: false
#| tbl-cap: UCSF Randomization

ucsf_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_ucsf AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 3
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

ucsf_random_plot <- ucsf_random_plot |>
    left_join(ucsf_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    ucsf_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### UAB

```{r}
#| label: uab randomization plot
#| echo: false
#| fig-cap: UAB Submissions by Clinician and Randomization

# query the data
uab_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_uab AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 4
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

uab_random_plot <- uab_random_plot |>
    left_join(uab_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_12 <- ggplot(
    data = uab_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = position_dodge2(width = 10, preserve = "total")
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("03/18/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_12, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: uab randomization table
#| echo: false
#| tbl-cap: UAB Randomization

uab_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_uab AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 4
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

uab_random_plot <- uab_random_plot |>
    left_join(uab_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    uab_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### UTSW

```{r}
#| label: utsw randomization plot
#| echo: false
#| fig-cap: UTSW Submissions by Clinician and Randomization

# query the data
utsw_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_utsw AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 5
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

utsw_random_plot <- utsw_random_plot |>
    left_join(utsw_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_12 <- ggplot(
    data = utsw_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = position_dodge2(width = 10, preserve = "total")
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("04/04/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_12, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: utsw randomization table
#| echo: false
#| tbl-cap: utsw Randomization

utsw_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_utsw AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 5
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

utsw_random_plot <- utsw_random_plot |>
    left_join(utsw_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    utsw_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### UTH LBJ

```{r}
#| label: lbj randomization plot
#| echo: false
#| fig-cap: UTH Houston LBJ Submissions by Clinician and Randomization

# query the data
lbj_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_lbj AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 6
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

lbj_random_plot <- lbj_random_plot |>
    left_join(lbj_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_12 <- ggplot(
    data = lbj_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = position_dodge2(width = 10, preserve = "total")
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("03/26/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_12, tooltip = c("x", "fill", "color"))
```

```{r}
#| label: lbj randomization table
#| echo: false
#| tbl-cap: lbj Randomization

lbj_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_lbj AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 6
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

lbj_random_plot <- lbj_random_plot |>
    left_join(lbj_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    lbj_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

### UTH UTP

```{r}
#| label: utp randomization plot
#| echo: false
#| fig-cap: UTH Houston UT Physicians Submissions by Clinician and Randomization

# query the data
utp_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        ar_aps_report_date as date,
        ar_clinician_utp AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 7
    GROUP BY clinician_id, date
    ORDER BY date ASC;
    "
))

utp_random_plot <- utp_random_plot |>
    left_join(utp_clinician, by = "clinician_id") |>
    select(num, date, clinician_name, clinician_randomized)

chart_12 <- ggplot(
    data = utp_random_plot,
    aes(y = num, x = date)
) +
    geom_point(
        aes(fill = clinician_randomized, color = clinician_name, size = 5),
        position = position_dodge2(width = 10, preserve = "total")
    ) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    geom_vline(
        xintercept = as.numeric(as.Date("03/13/2025", format = "%m/%d/%Y")),
        linetype = "dashed",
        color = "darkblue"
    ) +
    scale_y_continuous(guide = guide_axis(minor.ticks = FALSE))

ggplotly(chart_12, tooltip = c("x", "fill"))
```

```{r}
#| label: utp randomization table
#| echo: false
#| tbl-cap: utp Randomization

utp_random_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_clinician_utp AS clinician_id
    FROM 'APS-BL'
    WHERE ar_institution == 7
    GROUP BY clinician_id
    ORDER BY num ASC;
    "
))

utp_random_plot <- utp_random_plot |>
    left_join(utp_clinician, by = "clinician_id") |>
    select(num, perc, clinician_name, clinician_randomized)

datatable(
    utp_random_plot,
    colnames = c(
        "Number of Submissions",
        "Number of Submissions (%)",
        "Clinician",
        "Randomized"
    )
) |>
    formatPercentage("perc", 2)
```

# Demographics {orientation="rows"}

## Row {.tabset}

### Gender

```{r}
#| label: gender plot
#| echo: false
#| fig-cap: Gender

# query the data
gender_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_sex AS gender
    FROM 'APS-BL'
    GROUP BY gender
    ORDER BY gender ASC;
    "
))

# replace uninformative columns with string names
gender_plot <- gender_plot |>
    left_join(gender, by = "gender") |>
    select(num, perc, gender_label)

chart_3 <- ggplot(
    data = gender_plot,
    aes(y = gender_label, x = num)
) +
    geom_col(aes(fill = gender_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")


ggplotly(chart_3, tooltip = c("x"))
```

```{r}
#| label: gender table
#| echo: false
#| tbl-cap: Gender

datatable(gender_plot, colnames = c("Number", "Number (%)", "Gender")) |>
    formatPercentage("perc", 2)
```

### Relationship Status
```{r}
#| label: relationship status plot
#| echo: false
#| fig-cap: Relationship Status

# query the data
rel_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_relationship AS rel_status
    FROM 'APS-BL'
    GROUP BY rel_status
    ORDER BY rel_status ASC;
    "
))

# replace uninformative columns with string names
rel_plot <- rel_plot |>
    left_join(rel_status, by = "rel_status") |>
    select(num, perc, rel_status_label)

chart_4 <- ggplot(
    data = rel_plot,
    aes(y = rel_status_label, x = num)
) +
    geom_col(aes(fill = rel_status_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")


ggplotly(chart_4, tooltip = c("x"))
```

```{r}
#| label: relationship status table
#| echo: false
#| tbl-cap: Relationship Status

datatable(
    rel_plot,
    colnames = c("Number", "Number (%)", "Relationship Status")
) |>
    formatPercentage("perc", 2)
```

### Race

```{r}
#| label: race plot
#| echo: false
#| fig-cap: Race

# query the data
race_plot <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT 
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        CASE 
        WHEN ar_race___1 = 1 THEN 1
        WHEN ar_race___2 = 1 THEN 2
        WHEN ar_race___3 = 1 THEN 3
        WHEN ar_race___4 = 1 THEN 4
        WHEN ar_race___5 = 1 THEN 5
        WHEN ar_race___98 = 1 THEN 98
        END AS race
    FROM 'APS-BL'
    GROUP BY race
    ORDER BY race ASC;
    "
))

# replace uninformative columns with string names
race_plot <- race_plot |>
    left_join(race, by = "race") |>
    select(num, perc, race_label)

chart_5 <- ggplot(
    data = race_plot,
    aes(y = race_label, x = num)
) +
    geom_col(aes(fill = race_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")


ggplotly(chart_5, tooltip = c("x"))
```

```{r}
#| label: race table
#| echo: false
#| tbl-cap: Race

datatable(race_plot, colnames = c("Number", "Number (%)", "Race")) |>
    formatPercentage("perc", 2)
```

### Ethnicity
```{r}
#| label: hispanic plot
#| echo: false
#| fig-cap: Hispanic

# query the data
hispanic_plot <- as.data.frame(dbGetQuery(
    con,
    "SELECT
        COUNT(form_id) AS num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_hispanic AS hispanic
    FROM 'APS-BL'
    GROUP BY hispanic
    ORDER BY hispanic ASC;
    "
))

# replace uninformative columns with string names
hispanic_plot <- hispanic_plot |>
    left_join(hispanic, by = "hispanic") |>
    select(num, perc, hispanic_label)

chart_6 <- ggplot(
    data = hispanic_plot,
    aes(y = hispanic_label, x = num)
) +
    geom_col(aes(fill = hispanic_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")


ggplotly(chart_6, tooltip = c("x"))
```

```{r}
#| label: hispanic table
#| echo: false
#| tbl-cap: Ethnicity

datatable(hispanic_plot, colnames = c("Number", "Number (%)", "Hispanic")) |>
    formatPercentage("perc", 2)
```

# Clinical {orientation="rows"}

## Row {.tabset}

### Visit Reason

```{r}
#| label: visit reason plot
#| echo: false
#| fig-cap: Reason for Visit

# query the data
reason_plot <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT
        COUNT(form_id) as num_visits,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        ar_visit_reason as reason
    FROM 'APS-BL'
    GROUP BY reason
    ORDER BY num_visits ASC;
    "
))

# replace uninformative columns with string names
reason_plot <- reason_plot |>
    left_join(reason, by = "reason") |>
    select(num_visits, perc, reason_label)

chart_7 <- ggplot(
    data = reason_plot,
    aes(x = num_visits, y = reason_label)
) +
    geom_col(aes(fill = reason_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")

ggplotly(chart_7, tooltip = c("x"))
```

```{r}
#| label: visit reason table
#| echo: false
#| tbl-cap: Reason for Visit

datatable(
    reason_plot,
    colnames = c("Number", "Number (%)", "Reason for Visit")
) |>
    formatPercentage("perc", 2)
```

### Cognitive Impairment

```{r}
#| label: cognitive impairment plot
#| echo: false
#| fig-cap: Cognitive Impairment

# query the data
cog_imp_plot <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT
        COUNT(form_id) as num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        CASE
        WHEN ar_dx_mci_dementia___0 = 1 THEN 0
        WHEN ar_dx_mci_dementia___1 = 1 THEN 1
        WHEN ar_dx_mci_dementia___2 = 1 THEN 2
        WHEN ar_dx_mci_dementia___77 = 1 THEN 77
        ELSE 'Unknown'
        END as cog_imp
    FROM 'APS-BL'
    GROUP BY cog_imp
    ORDER BY num ASC;
    "
))

# replace uninformative columns with string names
cog_imp_plot <- cog_imp_plot |>
    left_join(cog_imp, by = "cog_imp") |>
    select(num, perc, cog_imp_label)

chart_8 <- ggplot(
    data = cog_imp_plot,
    aes(x = num, y = cog_imp_label)
) +
    geom_col(aes(fill = cog_imp_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")

ggplotly(chart_8, tooltip = c("x"))
```

```{r}
#| label: cognitive impairment table
#| echo: false
#| tbl-cap: Cognitive Impairment

datatable(
    cog_imp_plot,
    colnames = c("Number", "Number (%)", "Cognitive Impairment Diagnosis")
) |>
    formatPercentage("perc", 2)
```

### Functional Status

```{r}
#| label: functional status plot
#| echo: false
#| fig-cap: Functional Status

# query the data
func_status_plot <- as.data.frame(dbGetQuery(
    con,
    "
    SELECT
        COUNT(form_id) as num,
        COUNT(form_id) / SUM(COUNT(form_id)) OVER() as perc,
        CASE
        WHEN ar_functional_status___1 = 1 THEN 1
        WHEN ar_functional_status___2 = 1 THEN 2
        WHEN ar_functional_status___3 = 1 THEN 3
        WHEN ar_functional_status___4 = 1 THEN 4
        WHEN ar_functional_status___5 = 1 THEN 5
        WHEN ar_functional_status___98 =  1 THEN 98
        WHEN ar_functional_status___77 = 1 THEN 77
        ELSE NULL
        END as func_status
    FROM 'APS-BL'
    GROUP BY func_status
    ORDER BY num ASC;
    "
))

# replace uninformative columns with string names
func_status_plot <- func_status_plot |>
    left_join(func_status, by = "func_status") |>
    select(num, perc, func_status_label)

chart_9 <- ggplot(
    data = func_status_plot,
    aes(x = num, y = func_status_label)
) +
    geom_col(aes(fill = func_status_label)) +
    theme(
      legend.position = "none", 
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    ) +
    scale_fill_brewer(palette = "Dark2", na.value = "grey50")

ggplotly(chart_9, tooltip = c("x"))
```

```{r}
#| label: functional status table
#| echo: false
#| tbl-cap: functional status

datatable(
    func_status_plot,
    colnames = c("Number", "Number (%)", "Functional Status")
) |>
    formatPercentage("perc", 2)
```

```{r}
#| label: close db connection
#| echo: false

dbDisconnect(con, shutdown = TRUE)
```